Light Transport Techniques for Tensor Field Visualization

### 2019-08-07 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Fundamentals - Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{u(x)}\|_2
$\\
{\scriptsize where $\| A\| _2 = \sqrt{\lambda_{\max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measures gradient of flow map $\nabla\mathbf{u(x)}$
	\item FTLE field responds largest where path lines diverge
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\caption*{Double Gyre Field}\bigskip
\begin{minipage}{\textwidth}
{\scriptsize a)}
\centering
\includegraphics[height=0.25\textwidth]{diverge.png}
\end{minipage}
\begin{minipage}{\textwidth}
{\scriptsize b)}
\centering
\includegraphics[height=0.25\textwidth]{ftle.png}
\caption*{a) Vector field, b) FTLE field}
\end{minipage}
\begin{minipage}{0.05\textwidth}
\centering
\source{http://tiny.cc/2zbjaz}
\end{minipage}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

>>>>

\frame{
\frametitle{{Introduction - Tensor Fields}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{itemize}
	\item tensor-valued function: $\mathop{t_{ij}\mathbf{(x)}\colon} \mathbf{x}\mapsto t$, with $\mathbf{x}\in\mathcal{R}^n$: location vector
	\bigskip
	\item tensor fields can be visualized by:
	\begin{itemize}
		\item a) glyphs
		\item b) tensor field lines (TFLs)\\ $\Rightarrow$ streamlines for eigenvector fields
		\item c) scalar measures:\\ anisotropy index, tensor magnitude
	\end{itemize}
	\bigskip
	\item examples: stress tensor

\end{itemize}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\caption*{\textit{Random tensor field}}\bigskip
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[height=\textwidth]{random-global.png} {\scriptsize a) Glyphs}
\end{minipage}
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[height=\textwidth]{random-global-TFL.png} {\scriptsize b) Tensor field lines}
\end{minipage}
\end{figure}

\end{column}
\end{columns}

} % END OF FRAME
